%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\begin{document}

\header{Aaron}{ Kelly-Barker} % Your name and current job title/field


%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
1140 County Road 11, 
Picton, Ontario,
K0K2T0 Canada
~
613-919-3701
~
\href{mailto:aaron.kelly.barker@gmail.com}{aaronkellybarker@gmail.com}
\href{ca.linkedin.com/in/ackellyb/}{ca.linkedin.com/in/ackellyb}
\href{https://github.com/ackellyb}{github.com/ackellyb}
\section{programming}
C\#, Scala, Python
MySQL, C++, Java,
R, MatLab, LaTex, 
HTML, Powershell 
\& Batch Scripting
\end{aside}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\begin{entrylist}
%------------------------------------------------
\entry
{Sep. 2014--Apr. 2015}
{PALANTIR}
{Palo Alto, USA}
{\emph{Internal Tools Developer} \\
\begin{itemize}
	\item Had weekyl support shifts
	\item Stash, arifactory, applications, jenkins and bamboo that add value to developer work force of 1500
	\item Plugin to search through stash pull requests
	\item 
\end{itemize}
}
\end{entrylist}

\begin{entrylist}
%------------------------------------------------
\entry
{Jan. 2014--Apr. 2014}
{WORK MARKET INC.}
{New York City, USA}
{\emph{Software Engineering Intern} \\
\begin{itemize}
	\item Worked on the self-titled web-app Work Market, used by freelancers to find jobs. Was part of the core architecture team
	\item Technology stack included: Java, Spring and Hibernate for back-end, JavaScript, Less and underscore for front-end, and  MySQL and Apache Solr for data persistence
	\item Independently created a forum for Work Market users. Forum was created entirely from scratch. Features implemented in the forums include search, administrative control over posts, and the ability to follow posts 
	\item Built a service to provide interoperability between Work Market and Indeed.com
	\item Almost 100\% JUnit and integation test coverage for all new code 
	\item Bug squishing in all areas of Work Market, including front-end, back-end and mobile bugs
\end{itemize}
}
\end{entrylist}

\begin{entrylist}
%------------------------------------------------
\entry
{May 2013--Aug. 2013}
{CANADIAN IMPERIAL BANK OF COMMERCE}
{Toronto, Canada}
{\emph{Fixed Income Analytics Developer} \\
\begin{itemize}
	\item Worked on Phoenix, the system used by investment traders to analyze data. Focused on automation of Phoenix build and deployment
	\item Technology stack included: C\# for back-end, Python and Powershell for scripting, MySQL for data persistence, and MSBuild for build scripting
	\item Automated the build and deployment process of Phoenix, reducing the complex, time consuming process to a single command
	\item Created an application to generate release documentation, which pulled relevant release data from JIRA tickets to populate the documents
	\item Created administrative page to check data for incorrectly formed data
\end{itemize}
}
\end{entrylist}

\begin{entrylist}
%------------------------------------------------
\entry
{Sep. 2012--Dec. 2012}
{LEYSIN AMERICAN SCHOOL}
{Leysin, Switzerland}
{\emph{IT Assistant} \\
\begin{itemize}
	\item Provided trouble shooting for OSX environment and related software
	\item Co-led research into computer issues which had ot been encountered before
	\item Researched and presented a report on bottlenecks in interdepartmental communication and how to remove them
	\item Became very good at saying "Have you tried turning it off and on again?" 
\end{itemize}
}
\end{entrylist}

\begin{entrylist}
%------------------------------------------------
\entry
{Jan. 2012--Apr. 2012}
{GROUPTHINQ SOLUTIONS}
{Toronto, Canada}
{\emph{Back-End Developer} \\
\begin{itemize}
	\item Worked as the sole developer on an "instant task collaboration client", named Q
	\item Technology stack included: Scala and Java for back-end, Javascript  and CSS for front-end and MySQL for data persistance
	\item Implemented email parsing within Q, allowing Q to perform actions based on the \\ content of an email it receives 	
	\item Extended the in-client search to allow Boolean logic searching
	\item General optimizations and refactoring of the source code, along with bug squishing
\end{itemize}
}
\end{entrylist}



%----------------------------------------------------------------------------------------
%	VOLUNTEER SECTION
%----------------------------------------------------------------------------------------

\section{Volunteer Work}

\begin{entrylist}

%------------------------------------------------
\entry
{Apr. 2015--Aug. 2015}
{GLOW CENTRE FOR SEXUAL AND GENDER DIVERSITY}
{Waterloo, Canada}
{\emph{Social Media and Marketing Director} \\
\begin{itemize}
	\item Managed the Glow social media presence on Twitter, Facebook and Instagram
	\item Created and ran marketing campaigns to 
\end{itemize}
}

%------------------------------------------------
\entry
{Sep. 2011--Aug. 2014}
{GLOW CENTRE FOR SEXUAL AND GENDER DIVERSITY}
{Waterloo, Canada}
{\emph{General Service Volunteer} \\
\begin{itemize}
	\item Manned educational booths
	\item Ran social events for general public
	\item Kept office hours for 2 hours every week
\end{itemize}
}

%------------------------------------------------
\entry
{May 2012-- May 2013}
{FEDERATION OF STUDENTS}
{Waterloo, Canada}
{\emph{Student Technology Advisory Committee Student At-Large} \\
\begin{itemize}
	\item Voted by a panel of Federation of Student executives to represent the student body at Student Technology Advisory Committee meetings
	\item Advised on current technology issues faced by the school
\end{itemize}
}

%------------------------------------------------
\entry
{Sep. 2012--Dec. 2012}
{LEYSIN AMERICAN SCHOOL}
{Leysin, Switzerland}
{\emph{Tutor} \\
\begin{itemize}
	\item Tutored students in International Baccalaureate Mathematics and Physics
\end{itemize}
}


\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}
	
	%------------------------------------------------
	\entry
	{Sep. 2010--Now}
	{Honours Bachelor of Computer Science, Psychology Minor}
	{University of Waterloo}
	{Anticipated Graduation is December 2015 \\
		Course Projects:
		\begin{itemize}
			\item \course {Operating Systems}{OS/161}{Implemented system operations, system locks and memory management in a shell OS. Written in C}
			\item \course {Statistics}{Statistical Analysis Report}{Collected data from students about computer usage, and used R to perform analysis on it. Wrote a 17 page report in LaTex about the results}
			\item \course {Numerical Computation}{Sound Filtering}{Implemented high and low pass sound filters in MATLAB }
			\item \course {Foundations of Sequential Programs}{Compiler}{Built a compiler in C++, which compiled a modified form of C++ into MIPS}
		\end{itemize}
		
	}
	%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	MISCELLANEOUS SECTION
%----------------------------------------------------------------------------------------
\section{Miscellaneous}

\begin{entrylist}
\short
{Peer Support Training}
{May. 2014}

\short
{American Sign Language Basic Training}
{Sep. 2011 - Dec. 2011}

\short
{Emergency First Aid Training, CPR B}
{Mar. 2011}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}
Broadway and Off-Broadway theatre, PC + iOS gaming, Doctor Who,  Travelling
\end{document}