%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{resume-class} 
\begin{document}

\header{Aaron}{Kelly-Barker}{aaron.kelly.barker@gmail.com}{ackellyb}{ackellyb}{ackellyb}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\begin{sectionlist}
	%------------------------------------------------
	\entry
	{Aug. 2016--Present}
	{GREENLIGHT ESSENTIALS}
	{Lead Software Developer}
	{\emph {Kitchener, Canada}\\
		\begin{itemize}
		    \setlength{\itemsep}{0.2em}
			\item Created a build system in GulpJS. The system resulted in reproducible builds and utilization of asset optimization, allowing for easier debugging and smaller page weight across the board
			\item Revamped platform UI, focusing on user experience, easier navigation and quicker page loads. Originally written in React, and pivoted to regular ES6 Javascript when requirements changed
			\item Optimized intensive MongoDB queries, through code optimization, caching and indexing. Was able to bring the queries down from 6 seconds to less than a second
			\item Built webcrawlers in Python, which were used to supplement our film database with data about their social media and user interactions with it
		\end{itemize}
	}
	
	%------------------------------------------------
	\entry
	{Sep. 2014--Apr. 2015}
	{PALANTIR}
	{Internal Tools Software Developer}
	{\emph {Palo Alto, USA} \\
		\begin{itemize}
		    \setlength{\itemsep}{0.2em}
			\item Palantir had a problem with air-gapped dependencies being hard to locate, and unwiedy to manage. Created an indexer to locate all  artifacts, and act as an intermediate in dependency resolution
			\item Created plugin for Atlassian Stash to allow searching of Pull Requests in repositories, something that didn't exist before, and was helpful in managing feature requests in monolithic repos
		\end{itemize}
	}
	
	%------------------------------------------------
	\entry
	{Jan. 2014--Apr. 2014}
	{WORK MARKET INC.}
	{Core Architecture Software Developer}
	{\emph {New York City, USA}\\
		\begin{itemize}
		    \setlength{\itemsep}{0.2em}
			\item Planned, designed and coded a web forum. Built out the service in Java, frontend design in Javascript and Sass. Allowed users to create a sense of community on the platform
			\item Built a service to allow Work Market that interfaced with Indeed.com's API, allowing Work Market to post jobs to a new audience and expanding market reach
		\end{itemize}
	}
	
	%------------------------------------------------
	\entry
	{May 2013--Aug. 2013}
	{CIBC}
	{Software Developer}
	{\emph {Toronto, Canada} \\
		\begin{itemize}
		    \setlength{\itemsep}{0.2em}
			\item Automated build and deployment for a large application, condensing a complex and error-prone process into a single command, bringing down release time and failure rate
			\item Created an application to generate documentation needed for releases,\\dramatically cutting down time spent by the team on releases (CIBC loves a ton of release documentation)
		\end{itemize}
	}
	
\end{sectionlist}



%----------------------------------------------------------------------------------------
%	VOLUNTEER SECTION
%----------------------------------------------------------------------------------------
\vspace{-2.5\parskip}
\section{Volunteer Experience}


\begin{sectionlist}
	
	%------------------------------------------------
	\entry
	{Apr. 2015--Aug. 2015}
	{GLOW CENTRE FOR SEXUAL AND GENDER DIVERSITY}
	{Social Media and Marketing Director}
	{\emph{Waterloo, Canada} \\
		\begin{itemize}
		    \setlength{\itemsep}{0.2em}
			\item Managed the Glow social media presence on Twitter, Facebook and Instagram, expanding reach by 60\%
			\item Created marketing campaigns for our two main events, both which exceeded sales and engagement goals
		\end{itemize}
	}

\end{sectionlist}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\vspace{-2.5\parskip}
\section{Education}

\begin{sectionlist}
		
	%------------------------------------------------
	\education
	{Sep. 2010--Apr. 2016}
	{UNIVERSITY OF WATERLOO}
	{Honours Bachelor of Computer Science, Psychology Minor}
	
	%------------------------------------------------
\end{sectionlist}

\end{document}